Headgroup structure and cation binding in phosphatidylserine lipid bilayers

### 2019-08-21 Manuscript/manuscriptPS.tex
change format for number of lipids in a table in the main text

  lipid/counter-ions  & force field & {[}CaCl$_{2}${]}\,(M)  & N$_{{\rm l}}$  & N$_{{\rm w}}$  & \footnote{Number of Ca$^{2+}$ cations in addition to counter ions}N$_{{\rm c}}$  & T (K)  & t$_{{\rm sim}}$(ns)  & t$_{{\rm anal}}$ (ns)  & files\tabularnewline

@@

POPC:POPS (5:1)/Na$^{+}$  & CHARMM36 \cite{klauda10,venable13}  & 0  & 110 & 4620  & 0  & 298  & 2$\times$500  & 2$\times$100  & \citenum{charmm36pops+83popcT298KpiggotSODIUM} \tabularnewline
POPC:POPS (5:1)/K$^{+}$  & CHARMM36 \cite{klauda10,venable13}  & 0  & 110  & 4620  & 0  & 298  & 2$\times$500  & 2$\times$100  & \citenum{charmm36pops+83popcT298Kpiggot} \tabularnewline
POPC:POPS (5:1)/K$^{+}$  & CHARMM36 \cite{klauda10,venable13}  & 0  & 250  & 11207  & 0  & 298  & 200  & 180  & \citenum{POPC5POPS1noCaClCHARMM} \tabularnewline
POPC:POPS (5:1)  & CHARMM36 \cite{klauda10,venable13} / NBfix1 \cite{kim16}  & 0.26  & 250 & 11190  & 53  & 298  & 200  & 180  & \citenum{POPC5POPS1withCaClCHARMM} \tabularnewline
POPC:POPS (5:1)  & CHARMM36 \cite{klauda10,venable13} / NBfix1 \cite{kim16}  & 1.06  & 250 & 11174  & 214  & 298  & 200  & 180  & \citenum{POPC5POPS1with1MCaClCHARMM} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & CHARMM36 \cite{klauda10,venable13}  & 0  & 250  & 11207  & 0  & 320  & 400  & 300  & \citenum{POPC5POPS1CHARMMwithNBfixHan} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & CHARMM36 \cite{klauda10,venable13} / NBfix2 \cite{han2018graph}  & 0.14  & 250 & 11190  & 28  & 320  & 440  & 300  & \citenum{POPC5POPS1CHARMMwithNBfixHan} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & CHARMM36 \cite{klauda10,venable13} / NBfix2 \cite{han2018graph}  & 0.94  & 250 & 11174  & 189  & 320  & 440  & 300  & \citenum{POPC5POPS1CHARMMwithNBfixHan} \tabularnewline
POPC:POPS (1:1)/K$^{+}$  & CHARMM36 \cite{klauda10,venable13}  & 0  & 150  & 10785  & 0  & 298  & 200  & 180  & \citenum{POPC1POPS1noCaClCHARMM} \tabularnewline

@@

POPC:POPS (1:0)  & MacRog \cite{maciejewski14}  & 0  & 120 & 5120  & 0  & 298  & 200  & 150  & \citenum{macrogPOPC298K} \tabularnewline
POPC:POPS (5:1)/K$^{+}$  & MacRog \cite{maciejewski14}  & 0  & 120 & 5760  & 0  & 298  & 400 & 250 &  \citenum{POPCpopsMACROG}\tabularnewline
POPC:POPS (5:1)/K$^{+}$  & MacRog \cite{maciejewski14}  & 0.10  & 120  & 5760  & 10  & 298  & 600  & 300  & \citenum{POPCpopsMACROG} \tabularnewline
POPC:POPS (5:1)/K$^{+}$  & MacRog \cite{maciejewski14}  & 0.30  & 120  & 5760  & 31  & 298  & 600  & 300  & \citenum{POPCpopsMACROG} \tabularnewline
POPC:POPS (5:1)/K$^{+}$  & MacRog \cite{maciejewski14}  & 1.00  & 120 & 5760  & 104  & 298  & 600  & 300  & \citenum{POPCpopsMACROG} \tabularnewline
POPC:POPS (5:1)/K$^{+}$  & MacRog \cite{maciejewski14}  & 3.00  & 120 & 5760  & 311  & 298  & 600 & 300 & \citenum{POPCpopsMACROG}\tabularnewline

@@

POPC:POPS (5:1)/K$^{+}$  & Lipid14/17 \cite{dickson14,gould18} / ff99~\cite{aqvist90}  & 0  & 120  & 5760  & 0  & 298  & 2$\times$500  & 2$\times$200  & \citenum{POPCpopsLIPID17withKCI} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18} / ff99~\cite{aqvist90}  & 0  & 120 & 5760  & 0  & 298  & 2$\times$500  & 2$\times$200  & \citenum{POPCpopsLIPID17withNaCI} \tabularnewline
POPC:POPS (5:1)  & Lipid14/17 \cite{dickson14,gould18} / ff99~\cite{aqvist90}  & 0.50  & 120 & 5760  & 52  & 298  & 2$\times$500  & 2$\times$200  & \citenum{POPCpopsLIPID17withCaCl} \tabularnewline
POPC:POPS (5:1)  & Lipid14/17 \cite{dickson14,gould18} / ff99~\cite{aqvist90}  & 1.00  & 120  & 5760  & 104  & 298  & 2$\times$500  & 2$\times$200  & \citenum{POPCpopsLIPID17withCaCl} \tabularnewline
POPC:POPS (5:1)  & Lipid14/17 \cite{dickson14,gould18} / ff99~\cite{aqvist90}  & 2.00  & 120  & 5760  & 208  & 298  & 2$\times$500  & 2$\times$200  & \citenum{POPCpopsLIPID17withCaCl} \tabularnewline
POPC:POPS (5:1)  & Lipid14/17 \cite{dickson14,gould18} / ff99~\cite{aqvist90}  & 3.00  & 120 & 5760  & 311  & 298  & 2$\times$500  & 2$\times$200  & \citenum{POPCpopsLIPID17withCaCl} \tabularnewline
POPC:POPS (5:1)  & Lipid14/17 \cite{dickson14,gould18} / ff99~\cite{aqvist90}  & 4.00  & 120  & 5760  & 415  & 298  & 2$\times$500  & 2$\times$200  & \citenum{POPCpopsLIPID17withCaCl} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18} / Dang~\cite{smith94,dang06}  & 0  & 60 & 3600  & 0  & 298  & 1050  & 1000  & \citenum{lipid17_cacl_series} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18} / Dang~\cite{smith94,dang06}  & 0.08  & 60  & 3561  & 5  & 298  & 1050  & 1000  & \citenum{lipid17_cacl_series} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18} / Dang~\cite{smith94,dang06}  & 0.13  & 60  & 3561  & 8  & 298  & 1050  & 1000  & \citenum{lipid17_cacl_series} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18} / Dang~\cite{smith94,dang06}  & 0.20  & 60 & 3561  & 13  & 298  & 1050  & 1000  & \citenum{lipid17_cacl_series} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18} / Dang~\cite{smith94,dang06}  & 0.41  & 60 & 3522  & 26  & 298  & 1050  & 1000  & \citenum{lipid17_cacl_series} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18} / Dang~\cite{smith94,dang06}  & 0.62  & 60 & 3483  & 39  & 298  & 1050  & 1000  & \citenum{lipid17_cacl_series} \tabularnewline

@@

POPC:POPS (4:1)/Na$^{+}$  & Berger \cite{tieleman99,mukhopadhyay04}  & 0  & 102 & 4290  & 0  & 310  & 120  & 80  & \citenum{bergerPOPSPOPC4:1mixtureT310K} \tabularnewline

@@

data.}  & 104  & 4306  & 24  & 310  & 300  & 100  & \citenum{POPCpopsBERGERwith102mMCa} \tabularnewline
POPC:POPS (4:1)  & Berger \cite{tieleman99,mukhopadhyay04}  & 0.715\textsuperscript{\ref{noteBerger}}  & 104 & 4306  & 72  & 310  & 300  & 100  & \citenum{POPCpopsBERGERwith715mMCa} \tabularnewline

@@

POPC:POPS (5:1)/Na$^{+}$  & GROMOS-CKP\footnote{Force field parameters for PS lipids generated for this work, for full details see the supplementary information.} \cite{piggot12}  & 0  & 110 & 4620  & 0  & 298  & 2$\times$500  & 2$\times$100  & \citenum{POPCpopsGROMOSCKPwithNa} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & GROMOS-CKPM$^c$ \cite{piggot12}  & 0  & 110 & 4620  & 0  & 298  & 2$\times$500  & 2$\times$100  & \citenum{POPCpopsGROMOSCKPMwithNa} \tabularnewline

>>>>

  lipid/counter-ions  & force field & {[}CaCl$_{2}${]}\,(M)  & N$_{{\rm l}}$  & N$_{{\rm w}}$  & \footnote{Number of Ca$^{2+}$ cations in the system}N$_{{\rm c}}$  & T (K)  & t$_{{\rm sim}}$(ns)  & t$_{{\rm anal}}$ (ns)  & files\tabularnewline

@@

POPC:POPS (5:1)/Na$^{+}$  & CHARMM36 \cite{klauda10,venable13}  & 0  & 110:22 & 4620  & 0  & 298  & 2$\times$500  & 2$\times$100  & \citenum{charmm36pops+83popcT298KpiggotSODIUM} \tabularnewline
POPC:POPS (5:1)/K$^{+}$  & CHARMM36 \cite{klauda10,venable13}  & 0  & 110:22  & 4620  & 0  & 298  & 2$\times$500  & 2$\times$100  & \citenum{charmm36pops+83popcT298Kpiggot} \tabularnewline
POPC:POPS (5:1)/K$^{+}$  & CHARMM36 \cite{klauda10,venable13}  & 0  & 250:50  & 11207  & 0  & 298  & 200  & 180  & \citenum{POPC5POPS1noCaClCHARMM} \tabularnewline
POPC:POPS (5:1)  & CHARMM36 \cite{klauda10,venable13} / NBfix1 \cite{kim16}  & 0.26  & 250:50 & 11190  & 53  & 298  & 200  & 180  & \citenum{POPC5POPS1withCaClCHARMM} \tabularnewline
POPC:POPS (5:1)  & CHARMM36 \cite{klauda10,venable13} / NBfix1 \cite{kim16}  & 1.06  & 250:50 & 11174  & 214  & 298  & 200  & 180  & \citenum{POPC5POPS1with1MCaClCHARMM} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & CHARMM36 \cite{klauda10,venable13}  & 0  & 250:50  & 11207  & 0  & 320  & 400  & 300  & \citenum{POPC5POPS1CHARMMwithNBfixHan} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & CHARMM36 \cite{klauda10,venable13} / NBfix2 \cite{han2018graph}  & 0.14  & 250:50 & 11190  & 28  & 320  & 440  & 300  & \citenum{POPC5POPS1CHARMMwithNBfixHan} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & CHARMM36 \cite{klauda10,venable13} / NBfix2 \cite{han2018graph}  & 0.94  & 250:50 & 11174  & 189  & 320  & 440  & 300  & \citenum{POPC5POPS1CHARMMwithNBfixHan} \tabularnewline
POPC:POPS (1:1)/K$^{+}$  & CHARMM36 \cite{klauda10,venable13}  & 0  & 150:150  & 10785  & 0  & 298  & 200  & 180  & \citenum{POPC1POPS1noCaClCHARMM} \tabularnewline

@@

POPC:POPS (1:0)  & MacRog \cite{maciejewski14}  & 0  & 120:0 & 5120  & 0  & 298  & 200  & 150  & \citenum{macrogPOPC298K} \tabularnewline
POPC:POPS (5:1)/K$^{+}$  & MacRog \cite{maciejewski14}  & 0  & 120:24 & 5760  & 0  & 298  & 400 & 250 &  \citenum{POPCpopsMACROG}\tabularnewline
POPC:POPS (5:1)/K$^{+}$  & MacRog \cite{maciejewski14}  & 0.10  & 120:24  & 5760  & 10  & 298  & 600  & 300  & \citenum{POPCpopsMACROG} \tabularnewline
POPC:POPS (5:1)/K$^{+}$  & MacRog \cite{maciejewski14}  & 0.30  & 120:24  & 5760  & 31  & 298  & 600  & 300  & \citenum{POPCpopsMACROG} \tabularnewline
POPC:POPS (5:1)/K$^{+}$  & MacRog \cite{maciejewski14}  & 1.00  & 120:24 & 5760  & 104  & 298  & 600  & 300  & \citenum{POPCpopsMACROG} \tabularnewline
POPC:POPS (5:1)/K$^{+}$  & MacRog \cite{maciejewski14}  & 3.00  & 120:24 & 5760  & 311  & 298  & 600 & 300 & \citenum{POPCpopsMACROG}\tabularnewline

@@

POPC:POPS (5:1)/K$^{+}$  & Lipid14/17 \cite{dickson14,gould18} / ff99~\cite{aqvist90}  & 0  & 120:24  & 5760  & 0  & 298  & 2$\times$500  & 2$\times$200  & \citenum{POPCpopsLIPID17withKCI} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18} / ff99~\cite{aqvist90}  & 0  & 120:24 & 5760  & 0  & 298  & 2$\times$500  & 2$\times$200  & \citenum{POPCpopsLIPID17withNaCI} \tabularnewline
POPC:POPS (5:1)  & Lipid14/17 \cite{dickson14,gould18} / ff99~\cite{aqvist90}  & 0.50  & 120:24 & 5760  & 52  & 298  & 2$\times$500  & 2$\times$200  & \citenum{POPCpopsLIPID17withCaCl} \tabularnewline
POPC:POPS (5:1)  & Lipid14/17 \cite{dickson14,gould18} / ff99~\cite{aqvist90}  & 1.00  & 120:24  & 5760  & 104  & 298  & 2$\times$500  & 2$\times$200  & \citenum{POPCpopsLIPID17withCaCl} \tabularnewline
POPC:POPS (5:1)  & Lipid14/17 \cite{dickson14,gould18} / ff99~\cite{aqvist90}  & 2.00  & 120:24  & 5760  & 208  & 298  & 2$\times$500  & 2$\times$200  & \citenum{POPCpopsLIPID17withCaCl} \tabularnewline
POPC:POPS (5:1)  & Lipid14/17 \cite{dickson14,gould18} / ff99~\cite{aqvist90}  & 3.00  & 120:24 & 5760  & 311  & 298  & 2$\times$500  & 2$\times$200  & \citenum{POPCpopsLIPID17withCaCl} \tabularnewline
POPC:POPS (5:1)  & Lipid14/17 \cite{dickson14,gould18} / ff99~\cite{aqvist90}  & 4.00  & 120:24  & 5760  & 415  & 298  & 2$\times$500  & 2$\times$200  & \citenum{POPCpopsLIPID17withCaCl} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18} / Dang~\cite{smith94,dang06}  & 0  & 60:12 & 3600  & 0  & 298  & 1050  & 1000  & \citenum{lipid17_cacl_series} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18} / Dang~\cite{smith94,dang06}  & 0.08  & 60:12  & 3561  & 5  & 298  & 1050  & 1000  & \citenum{lipid17_cacl_series} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18} / Dang~\cite{smith94,dang06}  & 0.13  & 60:12  & 3561  & 8  & 298  & 1050  & 1000  & \citenum{lipid17_cacl_series} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18} / Dang~\cite{smith94,dang06}  & 0.20  & 60:12 & 3561  & 13  & 298  & 1050  & 1000  & \citenum{lipid17_cacl_series} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18} / Dang~\cite{smith94,dang06}  & 0.41  & 60:12 & 3522  & 26  & 298  & 1050  & 1000  & \citenum{lipid17_cacl_series} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & Lipid14/17 \cite{dickson14,gould18} / Dang~\cite{smith94,dang06}  & 0.62  & 60:12 & 3483  & 39  & 298  & 1050  & 1000  & \citenum{lipid17_cacl_series} \tabularnewline

@@

POPC:POPS (4:1)/Na$^{+}$  & Berger \cite{tieleman99,mukhopadhyay04}  & 0  & 102:26 & 4290  & 0  & 310  & 120  & 80  & \citenum{bergerPOPSPOPC4:1mixtureT310K} \tabularnewline

@@

data.}  & 104:26  & 4306  & 24  & 310  & 300  & 100  & \citenum{POPCpopsBERGERwith102mMCa} \tabularnewline
POPC:POPS (4:1)  & Berger \cite{tieleman99,mukhopadhyay04}  & 0.715\textsuperscript{\ref{noteBerger}}  & 104:26 & 4306  & 72  & 310  & 300  & 100  & \citenum{POPCpopsBERGERwith715mMCa} \tabularnewline

@@

POPC:POPS (5:1)/Na$^{+}$  & GROMOS-CKP\footnote{Force field parameters for PS lipids generated for this work, for full details see the supplementary information.} \cite{piggot12}  & 0  & 110:22 & 4620  & 0  & 298  & 2$\times$500  & 2$\times$100  & \citenum{POPCpopsGROMOSCKPwithNa} \tabularnewline
POPC:POPS (5:1)/Na$^{+}$  & GROMOS-CKPM$^c$ \cite{piggot12}  & 0  & 110:22 & 4620  & 0  & 298  & 2$\times$500  & 2$\times$100  & \citenum{POPCpopsGROMOSCKPMwithNa} \tabularnewline
